---
# This section between three dashes is the document metadata

title: "Notes and Exercises from"
subtitle: "The Book of R, by Tilman M. Davies"
date: "12/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Chapter 1

###How to check and assign working directory
###Environment variables

```{r}
# What is my working directory?
getwd()

# Let's pull environment username variable
Sys.getenv("USERNAME")

# Then we'll define the new working directory
# Note that R uses forward slashes, not back slashes.
paste("C:/Users/",Sys.getenv("USERNAME"),"/Desktop/R Working",sep="")

# Then set it
setwd(paste("C:/Users/",Sys.getenv("USERNAME"),"/Desktop/R Working",sep=""))

```

### Packages
```{r}
# Generally I use the drop-down menu to download packages.
# You can also use R code.

# Some packages may require R Tools, which is available here:
# https://cran.r-project.org/bin/windows/Rtools/rtools40.html
#install.packages("tidyverse")
update.packages()

```

### Help
# We can look up the help info for a function with ?.
# We can search the help for a keyword with ??
```{r}

?mean
# ??mean


```

## Chapter 2

### Arithmetic

### Exercise 2.1
```{r}

# a
((6*2.3)+42)/(3^(4.2-3.62))

# b
(-4)^2 + 2

# c
ex21.c <- c(25.2,15,16.44,15.3,18.6)
ex21.c <- ex21.c/2
sqrt (x=ex21.c)

# d
log(x=0.3)

# e
exp(log(x=0.3))

# f
-0.00000000423546322
    

```

### Assigning Objects
# You can use either <- or = to assign a value to an object

### Exercise 2.2
# a
x <- 3^2 * 4^(1/8)

# b
x <- x/2.33

# c
x2 <- (-8.2)*(10^(-15))

# d
x * x2

### Vectors, Sequence, Repetition
# We define a vector with the c function.
# The arguments can be numbers, or formulas, or even vectors.


```{r}
# Vectors
v1 <- c(12,14,2021)
v1
v1b <- c(v1, v1)
v1b
v2 <- 1:10
v2

# Sequences
v3 <- seq(from=10, to=100,by=10)
v3
v4 <- seq(from=0, to=100,length.out=5)
v4
v3b <- seq(from=100, to=10,by=-10)
v3b
v4b <- seq(from=100, to=0,length.out=5)
v4b

# Repetition
v5 <- rep(x=10,times=3)
v5
v6 <- rep(x=v1, times=3)
v6
v7 <- rep(x=v1, times=3, each=2)
v7

# Sort
v7s1 <- sort(v7, decreasing=TRUE)
v7s1
v7s2 <- sort(v7, decreasing=FALSE)
v7s2


#Length
length(x=v7s1)

```

#Let's clear variables
```{r}
rm(list=ls()) 
```

### Exercise 2.3
```{r}
# a
x213a <- seq(from=5, to=-11, by=-0.3)
x213a

# b
x213b <- sort(x213a,decreasing=FALSE)
x213b

# c
x213c1 <- c(-1,3,-5,7,-9)
x213c2 <- rep(x213c1, times=2, each=10)
x213c2

# d
x213d <- c(seq(from=6, to=12, b=1),rep(5.3,times=3),-3,seq(from=102,to=length(x213c2),length.out=9 ))
x213d

# e
x213e <- length(x213d)
x213e
```

### Subsets

```{r}
x <- c(5,6,7,8,9,10,11,12)

# We can pull the vector
x

# Or the second element
x[2]

# Or the vector, without the second element
x[-2]


#To identify the second-to-last element, we find the length of the vector
x[length(x=x)]

# then we just subtract one:
x[length(x=x)-1]

# We can remove it as follows:
x[-(length(x=x)-1)]

# Let's create an index of items in vector x

x_index <- seq(from=1,to=length(x),by=1)
x_index2 <- -x_index

x_index
x_index2

# We can feed this back to pull the original vector
x[x_index]

# Or an empty set, after removing all items
x[x_index2]

# We can pull every other item

x_index <- seq(from=1,to=length(x),by=2)
x_index
x[x_index]

# Or remove every other item, for the same result
x_index2 <- -seq(from=2,to=length(x),by=2)
x_index2
x[x_index2]


```

### Exercise 2.4
```{r}
# a

x214a <- c(seq(from=3,to=6,length.out=5),rep(c(2,-5.1,-33),times=1),(7/42)+2)
x214a

# b
x214b <- c(x214a[1],x214a[length(x214a)])
x214b

# c
x214c <- c(x214a[-1],x214a[-length(x214a)])
x214c

# d
x214d <- c(x214b[1],x214c,x214b[2])
x214d

#e
x214a <- sort(x214a,decreasing=FALSE)
x214e <- x214a

#f
x214f <- x214e[length(x214e):1]
x214f
sort(x214e,decreasing=TRUE)

#g
x214g <- c(rep(x214c[3],times=3),rep(x214c[6],times=4),rep(x214c[length(x214c)],times=1)   )
x214g

#h
x214h <- x214e
length(x214h)
x214h[c(1, 5:7,9)]
99:95
x214h[c(1, 5:7,length(x214h))] <- 99:95
x214h

```

### 
# When you perform an operation on two vectors with different lengths, r repeats the shorter one.
```{r}
x <- c(1,2,3,4,5,6,7,8)
x * c(1,0)


```

### Exercise 2.5

```{r}
# a
v215a1 <- c(2,0.5,1,2,0.5,1,2,0.5,1)
v215a2 <- c(1,2,3)
v215a1[v215a2]

# b

#     C = (5/9)(F - 32)
v215b1 <- c(45,77,20,19,101,120,212)
v215b2 <- (5/9)*(v215b1 - 32)

# c
v215c1 <- c(2,4,6)
v215c2 <- c(1,2)

# Produce 2,4,6,4,8,12
rep(v215c1,times=2)*rep(v215c2,each=3)

# d



```

## Chapter 3

## Chapter 4

## Chapter 5

## Chapter 6

## Chapter 7

## Chapter 8

## Chapter 9

## Chapter 10

## Chapter 11

## Chapter 12

## Chapter 13

## Chapter 14

## Chapter 15

## Chapter 16

## Chapter 17

## Chapter 18

## Chapter 19

## Chapter 20

## Chapter 21

## Chapter 22

## Chapter 23

## Chapter 24

## Chapter 25

## Chapter 26
